DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/evaluation.tex
camera latency.

\subsection{Summary}
So far, we have evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control, and made several observations.

>>>>

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra TX2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:patforms}
\end{table*}

\subsection{Summary of the Findings}
So far, we have evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control, and made several observations.

### 2017-10-05 paper/overview.tex
figure position
camera latency.

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/DeepPicar_platform}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|c|r|}
    \hline
    Item                    & Cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack \& misc.   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

@@

Nevertheless, the trained models were still able to achieve a reasonable
degree of accuracy, successfully navigating several different tracks 
we trained. The source code, build instruction, and a collection of
self-driving videos of the DeepPicar can be found at:
\url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/DeepPicar_platform}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{|c|r|}
    \hline
    Item                    & Cost (\$) \\
    \hline
    Raspberry Pi 3 Model B  & 35 \\
    New Bright 1:24 scale RC car       & 10 \\
    Playstation Eye camera  &  7 \\
    Pololu DRV8835 motor hat&  8 \\
    External battery pack \& misc.   & 10 \\
    \hline
    Total                   & 70 \\
    \hline
  \end{tabular}
  \caption{DeepPicar's bill of materials (BOM)}
  \label{tbl:carbom}
\end{table}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

@@

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is the time from the time the camera
sensor observes the scene to the time the computer actually read the
digitized image data. Unfortunately, this time can be substantially
long depending on the camera and the computer performance. We
experimentally measure DeepPicar's camera latency as
follows~\footnote{We follow the method and the tool found at
  https://www.makehardware.com/2016/03/29/finding-a-low-latency-webcam/}.
First, we point the DeepPicar's camera toward to a computer monitor, which is
conntected to the Raspberry Pi 3's HDMI output. We then launch a
simple program that overlay the current time with the camera's preview
screen on the monitor. Then, infinite number of time strings will be
shown on the monitor screen and the time difference between the two
successive time strings represent the camera
latency. Figure~\ref{fig:camera-latency} shows the captured moniotor
screen. The measured camera latency is about 300~350 ms. This is
significantly higher than a human's perception latency, which is known
to be as fast as 13 ms~\cite{ThomasBurger2015}. Higher camera latency
could negatively affect to the control performance as the DNN would
analyze stale scenes. In the future, we plan to identify and use
low-latency cameras.

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/camera_latency}
  \caption{Measuring DeepPicar's camera latency.}
  \label{fig:camera-latency}
\end{figure}

% https://www.pubnub.com/blog/2015-02-09-how-fast-is-realtime-human-perception-and-technology/

Despite aforementioned issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. The source code, build
instruction, and a collection of self-driving videos of the DeepPicar
can be found at: \url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}
